### 2014-08-21 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to fire/HRR description

The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located above the street level and two stories were located below the street level. The first and second floor (i.e., the two stories above street level) had a total interior floor area of 136~m$^2$ (1,468~ft$^2$). The interior walls were composed of gypsum board over insulated wood framing. The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (10 stairs down) or the second floor (5 stairs up).

@@

To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used. Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area. The basement primarily contained upholstered polyurethane furniture fuel items.

@@

@@

The HRR output quantity from FDS represents the predicted amount of combustion that would have occurred in the fire scenario, which depends on the amount of available fuel, oxygen, and ventilation. In the FDS simulations, the nominal HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location. As a result, the actual HRR in FDS can be lower than the specified HRR based on the ventilation conditions.

Figure~\ref{fig:hrr} shows the nominal HRR vs. time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}. The vertical line represents the time at which the first basement window on the rear side of the structure failed (342~s). The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with the timeline observations from the fire scenario. Note that the rear window failures were driven by the event timeline rather than failure temperature criteria.

@@

In Fig.~\ref{fig:hrr}, the XX line represents the baseline FDS simulation. The XX line represents an alternative simulation in which the basement door on the left side of the structure is open throughout the simulation. The XX line represents the nominal HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is approximately XX~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to XX~MW as the amount of oxygen inside the structure becomes limited. There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the ventilation openings where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at XX~s. After additional window failures occur at XX~s and XX~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to XX~MW before it decreases to approximately XX~MW. The HRR then increases towards a steady-state value.

>>>>

The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located above the street level and two stories were located below the street level. The first and second floor (i.e., the two stories above street level) had a total interior floor area of 136~m$^2$ (1,468~ft$^2$). The interior walls were composed of gypsum board over insulated wood framing. The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (ten~stairs down) or the second floor (five~stairs up).

@@

To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used. Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area. The basement primarily contained upholstered polyurethane furniture fuel items. The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.

@@

% The first 300~s of the HRR in the simulation follow the mattress HRR. After 300~s, the specified fire size is 20~MW.

@@

The HRR output quantity from FDS represents the predicted amount of combustion that would have occurred in the fire scenario, which depends on the amount of available fuel, oxygen, and ventilation. In the FDS simulations, a prescribed HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location. As a result, the actual HRR in FDS can be lower than the specified HRR based on the ventilation conditions.

Figure~\ref{fig:hrr} shows the prescribed HRR vs. time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}. The vertical line represents the time at which the first basement window on the rear side of the structure failed (342~s). The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with the timeline observations from the fire scenario. Note that the rear window failures were driven by the event timeline rather than failure temperature criteria.

@@

In Fig.~\ref{fig:hrr}, the XX line represents the baseline FDS simulation. The XX line represents an alternative simulation in which the basement door on the left side of the structure is open throughout the simulation. The XX line represents the prescribed HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is approximately XX~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to XX~MW as the amount of oxygen inside the structure becomes limited. There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the ventilation openings where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at XX~s. After additional window failures occur at XX~s and XX~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to XX~MW before it decreases to approximately XX~MW. The HRR then increases towards a steady-state value.
